---
title: "Untitled"
author: "Nanjun Wang"
date: "1/27/2017"
output: html_document
---
#Step0: Install and loading libraries
```{r, message=FALSE, warning=FALSE}

library(tm)
library(wordcloud)
library(RColorBrewer)
library(dplyr)
library(tidytext)
library(SnowballC)
library(ggplot2)
```

The notebook was prepared with the following envrionment setting:
```{r}
print(R.version)
```

#Step1: Loading Texts
```{r}
folder.path <- "/Users/ouminamikun/Desktop/Columbia/Spring 2017/ADS/Basic Text Mining/Data/inaugurals"
speeches <- list.files(path = folder.path, pattern = "*.txt")
prex.out <- substr(speeches, 6, nchar(speeches)-4)

ff.all<-Corpus(DirSource(folder.path))
inspect(ff.all[1])
```

#Step2: Preprocessing
For the speeches, I remove extra white space, convert all letters to the lower case, remove [stop words](https://github.com/arc12/Text-Mining-Weak-Signals/wiki/Standard-set-of-english-stopwords), removed empty words due to formatting errors, and remove punctuation. Then we compute the [Document-Term Matrix (DTM)](https://en.wikipedia.org/wiki/Document-term_matrix).  

```{r}
ff.all<-tm_map(ff.all, stripWhitespace)
ff.all<-tm_map(ff.all, content_transformer(tolower))
ff.all<-tm_map(ff.all, removeWords, stopwords("english"))
ff.all<-tm_map(ff.all, removeWords, character(0))
ff.all<-tm_map(ff.all, removePunctuation)

dtm <- DocumentTermMatrix(ff.all)
inspect(dtm[1:10,1:5])

dtm.tidy <- tidy(dtm) #a data.frame

dtm.sum <- summarise(group_by(dtm.tidy, term), sum(count))

```
#Step3: Word Clouds
```{r}
set.seed(142)
wordcloud(dtm.sum$term, 
          dtm.sum$`sum(count)`, 
          min.freq = 1,
          max.words = 100, 
          random.order = F,
          scale = c(5,0.01), 
          rot.per = 0.3,
          use.r.layout = T,
          colors = brewer.pal(6, "Dark2"))

```

#Step4: Compute TF-IDF weighted document-term matrices for individual speeches
As we would like to identify interesting words for each inaugural speech, we use [TF-IDF](https://en.wikipedia.org/wiki/Tf%E2%80%93idf) to weigh each term within each speech. It highlights terms that are more specific for a particular speech. 
```{r}

dtm.new <- DocumentTermMatrix(ff.all, 
                              control = list(weighting = function(x)
                                             weightTfIdf(x, normalize = F), stopwords = T  ))
dtm.new.tidy <- tidy(dtm.new)
```
#Step5: Interactive visualize key words in each speech
```{r}
library(shiny)
ui <- fluidPage(
  fluidPage(
    headerPanel(title = "Inaugural Word Clouds"),
  
    sidebarPanel(
      selectInput(inputId = "speeches", label = "Speeches", 
              choices = speeches, selected = speeches[5]),
      sliderInput(inputId = "nwords", label = "Number of words",3,
              min = 20, max = 200, value = 100, step = 20)
    ),
    
    mainPanel(
      plotOutput(outputId = "wordclouds", height = "400px")
    )
  )
)


server <- function(input, output){
  
  Data <- reactive({
    list(term <- dtm.new.tidy$term[dtm.new.tidy$document == as.character(input$speeches)],
        count <- dtm.new.tidy$count[dtm.new.tidy$document == as.character(input$speeches)])
    })
  output$wordclouds <- renderPlot( {
    wordcloud(Data()$term, 
              Data()$count,
              max.words = input$nwords,
              min.freq = 1,
              colors = brewer.pal(6, "Dark2"))
    }
  )
}

shinyApp(ui = ui, server = server)

```